The evolution of gene expression in the term placenta of viviparous mammals

### 2016-01-07 manuscript/manuscript.Rnw
discuss galili

\begin{table}[h]
  \tiny
<<top.50.mouse.expressed.genes,echo=FALSE,results="asis">>=
top.mouse.genes <- top.genes.table(species.name="mus musculus")
print(xtable(top.mouse.genes),
      booktabs=TRUE,
      floating=FALSE,
      sanitize.text.function=genes.table.sanitize,include.rownames=FALSE)
setkey(top.mouse.genes,"Gene symbol")
@ 
\caption{Expression in \ac{FPKM} of top 50 genes which are not ribosomal, 
mitochondrial, or whose human ortholog is a housekeeping gene in
  \textit{Mus musculus}}
\label{tab:top50_mouse_placenta}
\end{table}

@@

\subsubsection{\textit{Nannospalax galili} (Blind Mole Rat) Placenta Transcriptome}

\begin{table}[h]
  \tiny
<<top.50.n.galili.expressed.genes,echo=FALSE,results="asis">>=
top.galili.genes <- top.genes.table(species.name="nannospalax galili")
print(xtable(top.galili.genes),
      booktabs=TRUE,
      floating=FALSE,
      sanitize.text.function=genes.table.sanitize,include.rownames=FALSE)
setkey(top.galili.genes,"Gene symbol")
@ 
\caption{Expression in \ac{FPKM} of top 50 genes which are not ribosomal, 
mitochondrial, or whose human ortholog is a housekeeping gene in
  \textit{Nannospalax galili}}
\label{tab:top50_n_galili_placenta}
\end{table}

The 50 non-housekeeping genes with highest expression (by \ac{FPKM})
in the term placenta of \textit{Nannospalax galili} are shown in
\cref{tab:top50_n_galili_placenta} with a list of all highly expressed
genes in Supplemental \cref{tab:all_nannospalax_galili_placenta}.

\subsubsection{\textit{Spalax carmeli} (Blind Mole Rat) Placenta Transcriptome}

>>>>

\begin{table}[h]
  \tiny
<<top.50.mouse.expressed.genes,echo=FALSE,results="asis">>=
top.mouse.genes <- top.genes.table(species.name="mus musculus")
print(xtable(top.mouse.genes),
      booktabs=TRUE,
      floating=FALSE,
      sanitize.text.function=genes.table.sanitize,include.rownames=FALSE)
setkey(top.mouse.genes,"Gene symbol")
@ 
\caption{\tableexplanation{\mouse}{tab:all_mus_musculus_placenta}}
\label{tab:top50_mouse_placenta}
\end{table}

@@

\subsubsection{\galili Placenta Transcriptome}

\begin{table}[h]
  \tiny
<<top.50.n.galili.expressed.genes,echo=FALSE,results="asis">>=
top.galili.genes <- top.genes.table(species.name="nannospalax galili")
print(xtable(top.galili.genes),
      booktabs=TRUE,
      floating=FALSE,
      sanitize.text.function=genes.table.sanitize,include.rownames=FALSE)
setkey(top.galili.genes,"Gene symbol")
@ 
\caption{\tableexplanation{\galili}{tab:all_nannospalax_galili_placenta}}
\label{tab:top50_n_galili_placenta}
\end{table}

The 50 non-housekeeping genes with highest expression (by \ac{FPKM})
in the term placenta of \galili are shown in
\cref{tab:top50_n_galili_placenta} with a list of all highly expressed
genes in Supplemental \cref{tab:all_nannospalax_galili_placenta}.
Components of the annexin complex are highly expressed
(\Sexpr{gene.expression("nannospalax_galili","S100a6",complete=TRUE)},
\Sexpr{gene.expression("nannospalax_galili","S100a11",complete=TRUE)},
\Sexpr{gene.expression("nannospalax_galili","S100a10",complete=TRUE)},
and
\Sexpr{gene.expression("nannospalax_galili","Anxa2",complete=TRUE)}),
as are members of the thymosin family
(\Sexpr{gene.expression("nannospalax_galili","Tmsb4x",complete=TRUE)}
and
\Sexpr{gene.expression("nannospalax_galili","Tmsb10",complete=TRUE)}),
various cytoskeleton related proteins
(\Sexpr{gene.expression("nannospalax_galili","Actc1",complete=TRUE)},
\Sexpr{gene.expression("nannospalax_galili","Actg2",complete=TRUE)},
\Sexpr{gene.expression("nannospalax_galili","Acta2",complete=TRUE)},
\Sexpr{gene.expression("nannospalax_galili","Myl9",complete=TRUE)},
\Sexpr{gene.expression("nannospalax_galili","Vim",complete=TRUE)}), and
transmembrane protein of currently unknown function, 
\Sexpr{gene.expression("nannospalax_galili","Gm10134",complete=TRUE)}.

\subsubsection{\carmeli Placenta Transcriptome}
